Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Layout

\noindent
Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round of the last flight to be (0,1), satisfying criteria 9. This is a simple linear process. The schedule produced for 7 skippers and 6 boats is shown in Table \ref{tab2}.

\begin{table}[h]
%\vspace{-0.2cm}
\begin{center}
\begin{tabular}{cc} \\ 
flight & matches \\ \hline
0 & (0,6) (2,3) (4,5) \\
1 & (0,2) (4,1) (6,5) \\
2 & (2,1) (0,5) (6,3) \\
3 & (5,1) (0,3) (6,4) \\
4 & (3,5) (6,1) (2,4) \\
5 & (3,1) (0,4) (2,5) \\
6 & (3,4) (6,2) (0,1) \\ \hline
\end{tabular}
\end{center}
\caption{Round-robin schedule with 7 skippers, 6 boats and 7 flights. Result of stages 1, 2, and 3. It has 6 boat changes and imbalance 1. An example of imbalance is skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in position 1 and 1 (mid) in position 2 (last). Perfect balance would be 2 matches in each position, only achieved by skipper 2.}
\label{tab2}
\end{table}

>>>>

Stage 3 then takes as input the schedule produced in stage 2 and renames
skippers in the last round of the last flight to be (0,1), satisfying criteria
9. This is a simple linear process. The schedule produced for 7 skippers and 6
boats is shown in Table~\ref{tab2}.

\begin{table}[tb]
\begin{center}
\begin{tabular}{cc} \\
flight & matches \\ \hline
0 & (0,6) (2,3) (4,5) \\
1 & (0,2) (4,1) (6,5) \\
2 & (2,1) (0,5) (6,3) \\
3 & (5,1) (0,3) (6,4) \\
4 & (3,5) (6,1) (2,4) \\
5 & (3,1) (0,4) (2,5) \\
6 & (3,4) (6,2) (0,1) \\ \hline
\end{tabular}
\end{center}
\caption{Round-robin schedule with 7 skippers, 6 boats and 7 flights. Result of
stages 1, 2, and 3. It has 6 boat changes and imbalance 1. An example of
imbalance is skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in
position 1 and 1 (mid) in position 2 (last). Perfect balance would be 2 matches
in each position, only achieved by skipper 2.}
\label{tab2}
\end{table}
